Automatically Splitting a Staged Lambda Calculus

### 2015-07-10 paper/splitting.tex
attempting to lift some more discussion into 4.0

@@

\TODO ADD EQUIVALENCE FIGURE

@@

In this section, we consider a few exemplar cases 
from the proofs of \ref{lem:oneCorrect} and \ref{lem:twoCorrect}.

>>>>

Recall that a partial value $v$, by definition, has no remaining work in the first pass.
Since transfer of information between the stages occurs during the first pass, 
there can be no remaining internal communication between the stages of $v$.
In contrast, a term $e$ (at either \bbonem\ or \bbtwo) could still evaluate further in the first pass,
and so there may remain internal communication to happen between the stages of $e$.

This difference is why the second-stage output of either form of term splitting ($l.r$) is open on a variable,
while that of partial value splitting ($q$) is not.
Substitution for $l$ in $r$ is how communication between stages is represented in these outputs.

@@

@@

In this section, we consider a few exemplar cases 
from the proofs of \ref{lem:oneCorrect} and \ref{lem:twoCorrect}.
The equivalence relation ``$\equiv$'' is defined in \ref{fig:equiv}.
